 ---
title: "FM_Housing Workspace - Jake"
author: "Alex Voigt & Jake Peters"
date: "6/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(amap)
library(gtools)
library(useful)
library(cluster)
library(DEoptimR)
library(robustbase)
library(Gmedian)
library(RSpectra)

```


```{r}
FM_Housing_Raw <- read_csv(unz("../Data/FM_Housing_Raw.zip", "FM_Housing_Raw.csv"), col_types = cols(
  `Lease Term` = col_character(),
  `Directions` = col_character(),
  `Water Frontage Length` = col_integer()
))
```

```{r}
FM_Housing_Clean <- FM_Housing_Raw %>% select(-c("Property Type", "Card Format")) #All properties are Residential for both Property Type and Card Format variables
FM_Housing_Clean <- FM_Housing_Clean %>% select(-c("List Number", "Directions")) #Arbitrary values not useful for data mining
FM_Housing_Clean$`Year Built`[FM_Housing_Clean$`Year Built` < 1600 | FM_Housing_Clean$`Year Built` > 2021] <- NA
FM_Housing_Clean <- FM_Housing_Clean %>% mutate("List Price Change":=`List Price`-`Original List Price`)
FM_Housing_Clean <- FM_Housing_Clean %>% mutate("Sold/List Price Difference":=`Sold Price` - `List Price`)
FM_Housing_Clean <- FM_Housing_Clean %>% mutate("Sold/Original List Price Difference":=`Sold Price` - `Original List Price`)

```


```{r}
# kmeans Clustering with three variables
FM_Housing_Clean_Omit <- FM_Housing_Clean %>% filter(!is.na(`Geo Lon`) & !is.na(`Geo Lat`))
FM_Housing_kmeans2 <- FM_Housing_Clean_Omit %>% mutate(logprice = log(`Sold Price`, base = 1.8)) %>% mutate(milelong = (`Geo Lon`+97)/.0185) %>% mutate(milelat = (`Geo Lat` -46)/.0145) %>% select(logprice, milelong, milelat)
FM_Housing_kmeans2
```
# K-Means Cluster Analysis
#sum(is.na(FM_Housing_kmeans2))
#is.na(FM_Housing_kmeans2)
#apply(is.na(FM_Housing_kmeans2), 2, which)
#FM_Housing_kmeans2 <- na.omit(FM_Housing_kmeans2)
#FM_Housing_Clean_Omit <- FM_Housing_Clean %>% subset(FM_Housing_Clean, na.omit(select(logprice, milelong, milelat)))
#FM_Housing_Clean$`Geo Lon`[is.na(FM_Housing_Clean$`Geo Lon`)] <- mean(FM_Housing_Clean$`Geo Lon`,na.rm=TRUE)
#na.replace(FM_Housing_Clean$`Geo Lon`, mean(FM_Housing_Clean$`Geo Lon`))
#FM_Housing_Clean_Means <- na.replace(FM_Housing_Clean$`Geo Lat`, mean(FM_Housing_Clean$`Geo Lat`))

```{r}
fit <- Kmeans(FM_Housing_kmeans2, 21, nstart = 2, method = "manhattan") # 21 cluster solution
# get cluster means
aggregate(FM_Housing_kmeans2,by=list(fit$cluster),FUN=mean)
# append cluster assignment
FM_Housing_kmeans2 <- data.frame(FM_Housing_kmeans2, fit$cluster)

fit
FM_Housing_Clean_Omit <- FM_Housing_Clean_Omit %>% cbind(as.factor(fit$cluster)) %>% rename("cluster" = `as.factor(fit$cluster)`)

```

```{r}

ggplot() + geom_point(data=FM_Housing_Clean_Omit, mapping=aes(x=`Geo Lon`, y=`Geo Lat`), color=FM_Housing_Clean_Omit$`cluster`) + scale_color_gradient(low="yellow",high="red") + ylim(46.75, 46.95) + xlim(-96.95, -96.7)
ggplot(data = FM_Housing_Clean_Omit) + geom_point(mapping=aes(x=`Geo Lon`, y=`Geo Lat`),color=FM_Housing_Clean_Omit$`cluster`)  + scale_color_gradient(low="yellow",high="red") + ylim(46.75, 46.95) + xlim(-96.95, -96.7) + facet_wrap(~cluster)
```
k-medioids: clara
```{r}

clarax <- clara(FM_Housing_kmeans2, 72, samples=50)
clarax
```
```{r}
## Try 100 times *different* random samples -- for reliability:
nSim <- 100
nCl <- 3 # = no.classes
set.seed(421)# (reproducibility)
cl <- matrix(NA,nrow(xclara), nSim)
for(i in 1:nSim)
   cl[,i] <- clara(xclara, nCl, medoids.x = FALSE, rngR = TRUE)$cluster
tcl <- apply(cl,1, tabulate, nbins = nCl)
## those that are not always in same cluster (5 out of 3000 for this seed):
(iDoubt <- which(apply(tcl,2, function(n) all(n < nSim))))
if(length(iDoubt)) { # (not for all seeds)
  tabD <- tcl[,iDoubt, drop=FALSE]
  dimnames(tabD) <- list(cluster = paste(1:nCl), obs = format(iDoubt))
  t(tabD) # how many times in which clusters
}
# }

```

```{r}
#plot(clarax, ask = FALSE)
## plot clusters
#plot(x, col = clarax$cluster)
## plot centers
#points(clarax$centers, col = 1:2, pch = 8)
FM_Housing_Clean_Clara <- FM_Housing_Clean_Omit %>% cbind(as.factor(clarax$cluster)) %>% rename("cluster" = `as.factor(clarax$cluster)`)

ggplot() + geom_point(data=FM_Housing_Clean_Clara, mapping=aes(x=`Geo Lon`, y=`Geo Lat`), color=FM_Housing_Clean_Clara$`cluster`) + scale_color_gradient(low="yellow",high="red") + ylim(46.75, 46.95) + xlim(-96.95, -96.7)
FM_Housing_Clean_Clara %>% filter(`Sold Price` >= 10000 & `Sold Price` <= 700000) %>% ggplot() + geom_point(mapping=aes(x=`Geo Lon`, y=`Geo Lat`,color=`Sold Price`))  + scale_color_gradient(low="yellow",high="red") + ylim(46.75, 46.95) + xlim(-96.95, -96.7) + facet_wrap(~cluster)

```

K-medians clustering
```{r}
medians <- kGmedian(FM_Housing_kmeans2, 50, gamma=1, alpha=0.75, nstart = 10, nstartkmeans = 10,
iter.max = 20)
#clarax <- clara(FM_Housing_kmeans2, 72, samples=50)

```
K-medians plot
```{r}

FM_Housing_Clean_Median <- FM_Housing_Clean_Omit %>% cbind(as.factor(medians$cluster)) %>% rename("cluster" = `as.factor(medians$cluster)`)

ggplot() + geom_point(data=FM_Housing_Clean_Median, mapping=aes(x=`Geo Lon`, y=`Geo Lat`), color=FM_Housing_Clean_Median$`cluster`) + scale_color_gradient(low="yellow",high="red") + ylim(46.75, 46.95) + xlim(-96.95, -96.7)
FM_Housing_Clean_Median %>% filter(`Sold Price` >= 10000 & `Sold Price` <= 700000) %>% ggplot() + geom_point(mapping=aes(x=`Geo Lon`, y=`Geo Lat`,color=`Sold Price`))  + scale_color_gradient(low="yellow",high="red") + ylim(46.75, 46.95) + xlim(-96.95, -96.7) + facet_wrap(~cluster)

FM_Housing_Clean_Median %>% filter(`Sold Price` >= 10000 & `Sold Price` <= 700000) %>% ggplot() + geom_point(mapping=aes(x=`Geo Lon`, y=`Geo Lat`,color=`Map Area`))  +  ylim(46.75, 46.95) + xlim(-96.95, -96.7) + facet_wrap(~cluster)
ggplot(data=FM_Housing_Clean_Median %>% filter(`Geo Lon` >= -96.95, `Geo Lon` <= -96.7, `Geo Lat` >= 46.75, `Geo Lat` <= 46.95)) + geom_point( mapping=aes(x=`Geo Lon`, y=`Geo Lat`, color=`Map Area`))

```
```{r}

ggplot(data = FM_Housing_Clean_Median) + geom_bar(mapping = aes(`Map Area`))



```

